The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-07 SI.tex
orchestration section (#49)

@@

Each message call over the \yaq{} interface returns rapidly,
ensuring that client applications are not blocked. Some mes-
sages initiate long-running operations, e.g. motor motion and
sensor measurement. Separate messages are provided to re-
trieve results from e.g. sensor measurement.

>>>>

\section{Orchestration Examples}

Here we elaborate with detailed information about what orchestration looks like for \yaq{}.
As we discussed in Section 3 of the manuscript, \yaq{} is designed to accommodate a wide variety of orchestration tools and approaches.

\subsection{Raster Script}

For those unfamiliar with \yaq{}, the best orchestration example is a simple self-contained script.

\begin{codefragment}{Python}
import time
import yaqc
motor1 = yaqc.Client(port=38000)
motor2 = yaqc.Client(port=38001)
sensor = yaqc.Client(port=38002)
data = []
for m1 in range(-10, 10, 1):
    for m2 in range(0, 300, 5):
        motor1.set_position(m1)
        motor2.set_position(m2)
        for c in [motor1, motor2]:
            while c.busy():
                time.sleep(0.001)
        sensor.measure()
        while sensor.busy():
            time.sleep(0.001)
        reading = dict()
        reading["timestamp"] = time.time()
        reading["motor1"] = motor1.get_position()
        reading["motor2"] = motor2.get_position()
        reading.update(sensor.get_measured())
        data.append(reading)
\end{codefragment}

Here we are doing a two dimensional motor scan while collecting data from a sensor.
Motor one is stepping from -10 to 10, and motor two is scanning from 0 to 300.
Two examples of polling while not busy are used: the first to ensure that motors have stopped moving before sensors acquire, and the second to ensure that sensors stop collecting before the next motor motion happens.
This ``tick tock'' moving multiple motors, collecting sensor data, and repeating is a common pattern.

We believe that Python and the Scientific Python ecosystem is a powerfully simple tool for defining experimental procedures.
Lightweight scripts such as these are encouraged by the \yaq{} project.

\subsection{Landis}

We discussed the Landis Group and their WiQK reactor in Section 3 of the manuscript.
The Landis Group has defined several procedures for their flow reactor.
These procedures are highly idiosyncratic and are based on the particular tubing lengths and the flow topology of the reactor.
Each procedure involves articulating solenoid valves while injecting and withdrawing syringe pumps with a particular timing.
The Landis Group has written Python functions that drive this hardware using \yaq{}.
The functions parameterize the procedures in terms of chemically interesting variables like flow rate
and reaction time.

WiQK procedures and nascent graphical user interface can be found on GitHub at \\ \url{https://github.com/uw-madison-chem-shops/yaqc-wiqk}.

\subsection{Wright \& Bluesky}

@@

Each message call over the \yaq{} interface returns rapidly, ensuring that client applications are not blocked.
Some messages initiate long-running operations, \emph{e.g.} motor motion and sensor measurement.
Separate messages are provided to retrieve results from \emph{e.g.} sensor measurement.
